Learning constraints in tabular data

### 2016-05-12 Paper/ECAI/tabular.tex
rewriting paper strucutre

The question that we answer in this paper is: whether it is possible to discover or reconstruct structural constraints (relations, functions) in flat tabular spreadsheet data?
To answer this question we contribute a general-purpose algorithm and system for discovering such constraints. Furthermore, the algorithm accepts declarative specifications of the constraints and predicates of interest (the "bias") and covers both textual and numeric fields. It works in an unsupervised setting, as only the tabular data is provided and no examples need to be specified, and discovers column- and row-wise constraints.
We demonstrate the utility of our approach in an experimental evaluation.
Moreover, we sketch several application scenario's, such as autocompletion and error detection.
\\\\
This paper is organised as follows:
Section~2 introduces concepts relevant to our approach, Section~3 presents our problem statement, Section~4 describes our approach, the approach is evaluated in Section~5, in Section~6 we show how our system can be used for autocompletion and error detection, and we conclude in Section~7.

@@

\section{Formalization}
As we focus on spreadsheet data, we first introduce the general concepts of cells, group and constraint templates, using the (multi-table) sheet in Figure~\ref{fig:main_example} as running example.

@@

\section{Problem Statement}
The problem of learning constraints from tabular data can be seen as an inverse {\em constraint satisfaction problem} (CSP). A CSP consists of a set of constraints and the
task is to find assignments of values to the variables in the CSP so that all constraints are satisfied.
In the context of spreadsheets where variables could represent cells in tables, solving a corresponding CSP problem would mean completing the tables so that all constraints of the spreadsheet are satisfied.

@@

\newcommand{\tcl}{Tabular Constraint Learning}
%\newcommand{\ctl}{Condensed Tabular Constraint Learning}
\section{Approach to Tabular Constraint Learning}
This section describes our approach to \tcl. The main method takes \textit{groups} and {\template}s as input, and is described in Section~\ref{sec:algo}. We first explain how tables and groups can be extracted from raw spreadsheet data.

@@

\section{Evaluation}
\sergey{we need to add a summary of the dataset, avg number of constraints, cells, rows, columns}
In this section we experimentally validate our approach.
We studied various questions, most notably with what accuracy our algorithm can find essential constraints.

@@

\section{Applications}
In this section we will illustrate how various motivating applications could be realized using our system.

@@

\section{Conclusions}

>>>>

The question that we answer in this paper is: whether it is possible to discover or reconstruct structural constraints (relations, functions) in flat tabular spreadsheet data?
To answer this question we contribute a general-purpose algorithm and system for discovering such constraints. Furthermore, the algorithm accepts declarative specifications of the constraints and predicates of interest (the "bias") and covers both textual and numeric fields. It works in an unsupervised setting, as only the tabular data is provided and no examples need to be specified, and discovers column- and row-wise constraints.
We demonstrate the utility of our approach in an experimental evaluation.
Moreover, we sketch several application scenario's, such as autocompletion and error detection.
\\\\
This paper is organized as follows.
Section \ref{sec:formalization} introduces concepts relevant to our approach. Section \ref{sec:problem_statement} presents our problem statement. Section \ref{sec:approach} describes our approach. Section \ref{sec:evaluation} presents the evaluation of the approach. Section \ref{sec:applications} shows how our system can be used for autocompletion and error detection. Section \ref{sec:related_work} present an overview of the related work. And Section \ref{sec:conclusions} provides conclusions.

@@

\section{Formalization}\label{sec:formalization}
As we focus on spreadsheet data, we first introduce the general concepts of cells, group and constraint templates, using the (multi-table) sheet in Figure~\ref{fig:main_example} as running example.

@@

\section{Problem Statement}\label{sec:problem_statement}
The problem of learning constraints from tabular data can be seen as an inverse {\em constraint satisfaction problem} (CSP). A CSP consists of a set of constraints and the
task is to find assignments of values to the variables in the CSP so that all constraints are satisfied.
In the context of spreadsheets where variables could represent cells in tables, solving a corresponding CSP problem would mean completing the tables so that all constraints of the spreadsheet are satisfied.

@@

\newcommand{\tcl}{Tabular Constraint Learning}
%\newcommand{\ctl}{Condensed Tabular Constraint Learning}
\section{Approach to Tabular Constraint Learning}\label{sec:approach}
This section describes our approach to \tcl. The main method takes \textit{groups} and {\template}s as input, and is described in Section~\ref{sec:algo}. We first explain how tables and groups can be extracted from raw spreadsheet data.

@@

\section{Evaluation}\label{sec:evaluation}
\sergey{we need to add a summary of the dataset, avg number of constraints, cells, rows, columns}
In this section we experimentally validate our approach.
We studied various questions, most notably with what accuracy our algorithm can find essential constraints.

@@

\section{Applications}\label{sec:applications}
In this section we will illustrate how various motivating applications could be realized using our system.

@@

\section{Conclusions}\label{sec:conclusions}
